---
title: "2017 State Metrics Dashboard"

resource_files:
- data/2016_state_aggregation.csv
- data/2017_state_aggregation.csv
- data/2016_2015_sots_state_aggregation.csv
- data/upgrades_click_through.csv
- data/connectivity_click_through.csv
- data/fiber_click_through.csv
- data/affordability_click_through.csv
- data/current17_click_through.csv
- data/sots16_click_through.csv
- data/connectivity_targets.csv
- data/fiber_targets.csv
- data/wifi_click_through.csv
#- data/snapshots.csv
- data/tool_colors.csv
- data/date.csv

runtime: shiny
output:
  flexdashboard::flex_dashboard:
    smooth_scroll: yes
    vertical_layout: scroll
---
  
  
```{r setup, include=FALSE}
### Importing relevant libraries

## need to run compile this tool
library(flexdashboard) 
## need for render functions
library(shiny)
## most of the code is written using dplyr functions (e.g. %>% filter(), %>% summarise(), %>% select())
library(dplyr)
## need for highchart() vizes (eg. bar charts, box plots, scatter plots)
library(highcharter)
## need for supporting R markdown
library(rsconnect)
## for ggplot vizes (i.e. square colored box with status suchc as: 36 fiber targets)
library(ggplot2)
## need for datatables
library(DT)
## need for html use in code (I think)
library(htmltools)
```


```{r global, include = FALSE}
### Importing relevant data files

## state aggregated metrics for each year
state.agg.2017 <- read.csv("data/2017_state_aggregation.csv", as.is=T, header=T, stringsAsFactors=F)
state.agg.2016 <- read.csv("data/2016_state_aggregation.csv", as.is=T, header=T, stringsAsFactors=F)
state.agg.sots.2016 <- read.csv("data/2016_2015_sots_state_aggregation.csv", as.is=T, header=T, stringsAsFactors=F)

## click-throughs
current17_ct <- read.csv("data/current17_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
sots16_ct <- read.csv("data/sots16_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
upgrades_ct <- read.csv("data/upgrades_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
connectivity_ct <- read.csv("data/connectivity_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
fiber_ct <- read.csv("data/fiber_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
affordability_ct <- read.csv("data/affordability_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
wifi_ct <- read.csv("data/wifi_click_through.csv", as.is=T, header=T, stringsAsFactors=F)
## targets
connectivity_tar <- read.csv("data/connectivity_targets.csv", as.is=T, header=T, stringsAsFactors=F)
fiber_tar <- read.csv("data/fiber_targets.csv", as.is=T, header=T, stringsAsFactors=F)

## color data
colors <- suppressWarnings(read.csv("data/tool_colors.csv", as.is=T, header=T, stringsAsFactors=F))

## date
date.updated <- read.csv("data/date.csv", as.is=T, header=T, stringsAsFactors=F)
date.updated <- date.updated$date
```


```{r, include = FALSE}
### Setting up reactive data sets

## state metrics aggregation
state.agg.2016.sub <- reactive({state.agg.2016 %>% filter(postal_cd %in% input$state)})
state.agg.sots.2016.sub <- reactive({state.agg.sots.2016 %>% filter(postal_cd %in% input$state)})
state.agg.2017.sub <- reactive({state.agg.2017 %>% filter(postal_cd %in% input$state)})

## click-throughs
current17_ct_sub <- reactive({current17_ct %>% filter(postal_cd %in% input$state)})
sots16_ct_sub <- reactive({sots16_ct %>% filter(postal_cd %in% input$state)})
upgrades_ct_sub <- reactive({upgrades_ct %>% filter(postal_cd %in% input$state)})
connectivity_ct_sub <- reactive({connectivity_ct %>% filter(postal_cd %in% input$state)})
fiber_ct_sub <- reactive({fiber_ct %>% filter(postal_cd %in% input$state)})
affordability_ct_sub <- reactive({affordability_ct %>% filter(postal_cd %in% input$state)})
wifi_ct_sub <- reactive({wifi_ct %>% filter(postal_cd %in% input$state)})

## targets
connectivity_tar_sub <- reactive({connectivity_tar %>% filter(postal_cd %in% input$state)})
fiber_tar_sub <- reactive({fiber_tar %>% filter(postal_cd %in% input$state)})
```


State Summary {data-orientation=rows}
======================================================================
Row 
----------------------------------------------------------------------
### 
```{r}
renderValueBox({
  ## state lookup
  state_lookup <- data.frame(cbind(name=state.agg.2017$state_name), code=state.agg.2017$postal_cd, stringsAsFactors=F)
  state_lookup$name_caps <- toupper(state_lookup$name)
  ## making this global so we can use it in other sections as well
  state_name_caps <<- state_lookup$name_caps[state_lookup$code == state.agg.2017.sub()$postal_cd]
  valueBox(state_name_caps, paste("Date Updated:", date.updated, sep=" "))
})
```

### 2017 Population of Districts {.no-padding}
```{r}
renderValueBox({
  pop.districts.17 <- format(state.agg.2017.sub()$districts_population, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(pop.districts.17, color = colors$color[colors$label == 'districts'])
})
```

### 2017 Population of Schools {.no-padding}
```{r}
renderValueBox({
  pop.schools.17 <- format(state.agg.2017.sub()$schools_population, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(pop.schools.17, color = colors$color[colors$label == 'schools'])
})
```

### 2017 Population of Students {.no-padding}
```{r}
renderValueBox({
  pop.students.17 <- format(state.agg.2017.sub()$students_population, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(pop.students.17, color = colors$color[colors$label == 'students'])
})
```

Row 
-----------------------------------------------------------------------
### Select State 
```{r input}
state.agg.2017$postal_cd <- as.character(state.agg.2017$postal_cd)
selectInput('state', label="", choices=unique(state.agg.2017$postal_cd), selected="ALL")

#output$downloadData <- downloadHandler(
#  filename = function() {"data/snapshots.csv"},
#  content = function(file) {
#  write.csv(snapshots, file, row.names=F)
#  })
#downloadLink('downloadData', label = 'Download State Snapshot Data')

## paste below outside of this box when want to add the snapshot download
#***
#NOTE: Underlying Data Download will pull state metrics spreadsheet for all 50 states.
```



### [SotS 2015: % Clean Districts](#deep-dive-sots15)
```{r}
renderGauge({
  sots15 <- state.agg.sots.2016.sub()$sots15_districts_sample_perc
  gauge(sots15, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))})
```

### [SotS 2016: % Clean IA Districts](#deep-dive-sots16)
```{r}
renderGauge({
  sots16 <- state.agg.sots.2016.sub()$current16_districts_sample_perc
  gauge(sots16, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))})
```

### [Current 2017: % Clean IA Districts](#deep-dive-current17)
```{r}
renderGauge({
  current17 <- round((state.agg.2017.sub()$districts_clean_ia_sample / state.agg.2017.sub()$districts_population)*100, 0)
  gauge(current17, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))})
```

Row {data-height=350}
------------------------------------------------------------------------
### {.no-padding}
```{r, fig.width=1.5}
img(src = "figures/upgrades.png", height = "100%", width = "100%")
```

### [Districts Upgraded](#deep-dive-upgrades) {.no-padding}
```{r}
renderPlot({
  text <- format(state.agg.2017.sub()$districts_upgraded, big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("of ", format(state.agg.2017.sub()$districts_clean_upgrades_sample, big.mark = ",", nsmall = 0, scientific = FALSE),
                 " (", round((state.agg.2017.sub()$districts_upgraded / state.agg.2017.sub()$districts_clean_upgrades_sample)*100, 0), "%", ")", sep='')
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.16, label = text, size = 20, color = "white") +
    annotate("text",  x = 2.5, y = 24.65, label = text2, size = 16, color = "white") +
    theme(panel.background = element_rect(fill =  rgb(92/255, 0/255, 92/255, 0.8)),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

### Students Upgraded {.no-padding}
```{r}
renderPlot({
  text <- format(state.agg.2017.sub()$students_upgraded, big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("of ", format(state.agg.2017.sub()$students_clean_upgrades_sample, big.mark = ",", nsmall = 0, scientific = FALSE),
                 " (", round((state.agg.2017.sub()$students_upgraded / state.agg.2017.sub()$students_clean_upgrades_sample)*100, 0), "%", ")", sep='')
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.16, label = text, size = 17, color = "white") +
    annotate("text",  x = 2.5, y = 24.65, label = text2, size = 12, color = "white") +
    theme(panel.background = element_rect(fill = rgb(133/255, 50/255, 133/255, 0.9)),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```  

### Districts Upgraded Now Meeting Goals {.no-padding}
```{r}
renderPlot({
  text <- format(state.agg.2017.sub()$districts_upgraded_meeting_goals, big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("of ", format(state.agg.2017.sub()$districts_upgraded, big.mark = ",", nsmall = 0, scientific = FALSE),
                 " (", round((state.agg.2017.sub()$districts_upgraded_meeting_goals / state.agg.2017.sub()$districts_upgraded)*100, 0), "%", ")", sep='')
  text3 <- paste(format(state.agg.2017.sub()$students_upgraded_meeting_goals, big.mark = ",", nsmall = 0, scientific = FALSE), " students", sep='')
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.45, label = text, size = 17, color = "white") +
    annotate("text",  x = 2.5, y = 25.05, label = text2, size = 12, color = "white") +
    annotate("text",  x = 2.5, y = 24.45, label = text3, size = 12, color = "white") +
    theme(panel.background = element_rect(fill = rgb(178/255, 102/255, 178/255, 0.9)),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```
  
Row {data-height = 350}
------------------------------------------------------------------------
### {.no-padding}
```{r, fig.width=1.5}
img(src = "figures/connectivity.png", height = "100%", width = "100%")
```

### [Districts Meeting Connectivity Goals](#deep-dive-connectivity)
```{r}
renderHighchart({
  highchart() %>% hc_chart(type = 'column') %>% 
    hc_xAxis(categories = c(paste('Published SotS 2015 (n=', format(state.agg.sots.2016.sub()$sots15_districts_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Published SotS 2016 (n=', format(state.agg.sots.2016.sub()$current16_districts_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Current 2016 (n=', format(state.agg.2016.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Current 2017 (n=', format(state.agg.2017.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''))) %>%
    hc_yAxis(labels = list(format = '{value}%'), min = 0, max = 100) %>% 
    hc_add_series(data = c(state.agg.sots.2016.sub()$sots15_districts_mtg2014goal_perc,
      state.agg.sots.2016.sub()$current16_districts_mtg2014goal_perc,
      round((state.agg.2016.sub()$districts_meeting_2014_bw_goal / state.agg.2016.sub()$districts_clean_ia_sample)*100, 0),
      round((state.agg.2017.sub()$districts_meeting_2014_bw_goal / state.agg.2017.sub()$districts_clean_ia_sample)*100, 0)),
      dataLabels = list(enabled = TRUE, format = '{point.y}%')) %>% hc_legend(enabled = FALSE) %>% hc_colors(c(colors$color[colors$label == 'connectivity1']))
})
```

### [Connectivity Targets](#target-lists-connectivity) {.no-padding}
```{r}
renderPlot({
  val <- paste("Targets: ", format(state.agg.2017.sub()$district_bw_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$district_bw_targets / state.agg.2017.sub()$districts_population)*100, 0), "%)",
               
               "\nClean Targets: ", format(state.agg.2017.sub()$clean_district_bw_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$clean_district_bw_targets / state.agg.2017.sub()$districts_clean_ia_sample)*100, 0), "%)",
               
               "\nPotential Targets: ", format(state.agg.2017.sub()$district_bw_potential_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$district_bw_potential_targets / state.agg.2017.sub()$districts_population)*100, 0), "%)",
               
               "\nClean Potential Targets: ", format(state.agg.2017.sub()$clean_district_bw_potential_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$clean_district_bw_potential_targets / state.agg.2017.sub()$districts_clean_ia_sample)*100, 0), "%)", sep='')
  
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.15, label = val, size = 10, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'connectivity2']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

### Students Meeting Goal (Extrapolated) {.no-padding}
```{r}
renderPlot({
  ## calculate percentage of students meeting connectivity goal to extrapolate
  percentage.student.meeting.goal.2017 <- state.agg.2017.sub()$students_meeting_2014_bw_goal / state.agg.2017.sub()$students_clean_ia_sample
  text <- format(round(percentage.student.meeting.goal.2017 * state.agg.2017.sub()$students_population, 0),
                 big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("(", round(percentage.student.meeting.goal.2017*100, 0), "%)", sep='') 
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.15, label = text, size = 20, color = "white") +
    annotate("text",  x = 2.5, y = 24.85, label = text2, size = 15, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'connectivity3']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

Row {data-height = 350}
----------------------------------------------------------
### {.no-padding}
```{r, fig.width=1.5}
img(src = "figures/fiber.png", height = "100%", width = "100%")
```

### [Campuses on Fiber](#deep-dive-fiber)
```{r}
renderHighchart({
  ## calculate campuses on fiber
  highchart() %>% hc_chart(type = 'column') %>% 
    hc_xAxis(categories = c(paste('Published SotS 2015 (n=', format(state.agg.sots.2016.sub()$sots15_districts_pop, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Published SotS 2016 (n=', format(state.agg.sots.2016.sub()$current16_districts_pop, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Current 2016 (n=', format(state.agg.2016.sub()$districts_population, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Current 2017 (n=', format(state.agg.2017.sub()$districts_population, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''))) %>% 
    hc_yAxis(labels = list(format = '{value}%'), min = 0, max = 100) %>% 
    hc_add_series(data = c(state.agg.sots.2016.sub()$sots15_campuses_on_fiber_perc,
                  state.agg.sots.2016.sub()$current16_campuses_on_fiber_perc,
                  round((state.agg.2016.sub()$scalable_campuses / state.agg.2016.sub()$campuses_population)*100, 0),
                  round((state.agg.2017.sub()$scalable_campuses / state.agg.2017.sub()$campuses_population)*100, 0)),
                  dataLabels = list(enabled = TRUE, format = '{point.y}%')) %>% hc_legend(enabled = FALSE) %>% hc_colors(c(colors$color[colors$label == 'fiber1']))
})
```

### [Fiber Targets](#target-lists-fiber) {.no-padding}
```{r}
renderPlot({
  val <- paste("Targets: ", format(state.agg.2017.sub()$district_fiber_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$campus_fiber_targets / state.agg.2017.sub()$campuses_population)*100, 0), "%)",
               
               "\nClean Targets: ", format(state.agg.2017.sub()$clean_district_fiber_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$clean_campus_fiber_targets / state.agg.2017.sub()$campuses_clean_ia_sample)*100, 0), "%)",
               
               "\nPotential Targets: ", format(state.agg.2017.sub()$district_fiber_potential_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$campus_fiber_potential_targets / state.agg.2017.sub()$campuses_population)*100, 0), "%)",
               
               "\nClean Potential Targets: ", format(state.agg.2017.sub()$clean_district_fiber_potential_targets, big.mark = ",", nsmall = 0, scientific = FALSE),
               " (", round((state.agg.2017.sub()$clean_campus_fiber_potential_targets / state.agg.2017.sub()$campuses_clean_ia_sample)*100, 0), "%)", sep='')
  ## need to set min and max for y-axis so can label both the number and "targets"
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.15, label = val, size = 10, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'fiber2']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

### Campuses on Fiber (Extrapolated) {.no-padding}
```{r}
renderPlot({
  text <- format(round(state.agg.2017.sub()$scalable_campuses, 0), big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("of ", format(state.agg.2017.sub()$campuses_population, big.mark = ",", nsmall = 0, scientific = FALSE), sep='')
  text3 <- paste("(", format(round(state.agg.2017.sub()$campuses_population - state.agg.2017.sub()$scalable_campuses, 0), big.mark = ",", nsmall = 0, scientific = FALSE), " not on fiber)", sep='')
  text4 <- paste("Average Number of Campuses\n not on Fiber (of Targets): ", state.agg.2017.sub()$mean_unscalable_campuses_targets, sep="")
  
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.45, label = text, size = 17, color = "white") +
    annotate("text",  x = 2.5, y = 25.05, label = text2, size = 12, color = "white") +
    annotate("text",  x = 2.5, y = 24.75, label = text3, size = 12, color = "white") +
    annotate("text",  x = 2.5, y = 24.45, label = text4, size = 6, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'fiber3']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

Row {data-height = 350}
------------------------------------------------------------------------
### {.no-padding}
```{r, fig.width=1.5}
img(src = "figures/affordability.png", height = "100%", width = "100%")
```

### [Districts Meeting Affordability Goal](#deep-dive-affordability)
```{r}
renderHighchart({
  highchart() %>% 
    hc_chart(type = 'column') %>% 
    hc_xAxis(categories = c(paste('Published SotS 2015 (n=', format(state.agg.sots.2016.sub()$sots15_districts_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Published SotS 2016 (n=', format(state.agg.sots.2016.sub()$current16_districts_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Current 2016 (n=', format(state.agg.2016.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''),
      paste('Current 2017 (n=', format(state.agg.2017.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE), ')', sep=''))) %>% 
    hc_yAxis(labels = list(format = '{value}%'), min = 0, max = 100) %>% 
    hc_add_series(data = c(state.agg.sots.2016.sub()$sots15_districts_mtg_affordability_perc,
      state.agg.sots.2016.sub()$current16_districts_mtg_affordability_perc,
      round((state.agg.2016.sub()$districts_meeting_affordability / state.agg.2016.sub()$districts_clean_ia_sample)*100, 0),
      round((state.agg.2017.sub()$districts_meeting_affordability / state.agg.2017.sub()$districts_clean_ia_sample)*100, 0)),
      dataLabels = list(enabled = TRUE, format = '{point.y}%')) %>% hc_legend(enabled = FALSE) %>% hc_colors(c(colors$color[colors$label == 'affordability1'])) 
})
```

### Median Cost per Mbps {.no-padding}
```{r}
renderPlot({
  text <- paste("2016: $", round(state.agg.2016.sub()$median_ia_monthly_cost_per_mbps, 2), sep="")
  text2 <- paste("2017: $", round(state.agg.2017.sub()$median_ia_monthly_cost_per_mbps, 2), sep="")
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.15, label = text, size = 20, color = "white") +
    annotate("text",  x = 2.5, y = 24.75, label = text2, size = 20, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'affordability2']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

### Students Meeting Goal (Extrapolated) {.no-padding}
```{r}
renderPlot({
  ## calculate percentage of students meeting afforadability goal to extrapolate
  percentage.student.meeting.goal.2017 <- state.agg.2017.sub()$students_meeting_affordability / state.agg.2017.sub()$students_clean_ia_sample
  text <- format(round(percentage.student.meeting.goal.2017 * state.agg.2017.sub()$students_population, 0),
                 big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("(", round(percentage.student.meeting.goal.2017*100, 0), "%)", sep='')
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.15, label = text, size = 20, color = "white") +
    annotate("text",  x = 2.5, y = 24.85, label = text2, size = 15, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'affordability3']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

Row {data-height = 350}
------------------------------------------------------------------------
### {.no-padding}
```{r, fig.width=1.5}
img(src = "figures/wifi.png", height = "100%", width = "100%")
```

### [C2 Money Leftover (in Millions)](#deep-dive-wifi)
```{r}
renderHighchart({
  highchart() %>% hc_chart(type = 'column') %>% 
  hc_xAxis(categories = c('Current 2015', 'Current 2016', 'Current 2017')) %>% 
  hc_yAxis(labels = list(format = '${value}'), min=0, max=max(state.agg.2017.sub()$c2_remaining_2015/1000000,
                                                              state.agg.2017.sub()$c2_remaining_2016/1000000,
                                                              state.agg.2017.sub()$c2_remaining_2017/1000000, na.rm=T)) %>% 
  hc_add_series(data = c(round(state.agg.2017.sub()$c2_remaining_2015/1000000, 1),
                         round(state.agg.2017.sub()$c2_remaining_2016/1000000, 1),
                         round(state.agg.2017.sub()$c2_remaining_2017/1000000, 1)),
                dataLabels=list(enabled=TRUE, format='${point.y}')) %>%  hc_legend(enabled=FALSE) %>% hc_colors(c(colors$color[colors$label == 'wifi1']))
})
```

### Number of Districts with Adequate Wifi {.no-padding}
```{r}
renderPlot({
  ## calculate percentage of students meeting connectivity goal to extrapolate
  percentage.districts.with.wifi.2017 <- round((state.agg.2017.sub()$districts_with_wifi / state.agg.2017.sub()$districts_wifi_sample)*100, 0)
  text <- format(state.agg.2017.sub()$districts_with_wifi, big.mark = ",", nsmall = 0, scientific = FALSE)
  text2 <- paste("of ", format(state.agg.2017.sub()$districts_wifi_sample, big.mark = ",", nsmall = 0, scientific = FALSE), " (", percentage.districts.with.wifi.2017, "%", ")", sep="")
  ggplot() + ylim(24, 26) +
    annotate("text",  x = 2.5, y = 25.15, label = text, size = 20, color = "white") +
    annotate("text",  x = 2.5, y = 24.85, label = text2, size = 15, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'wifi2']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```

### Number of Districts WITHOUT Adequate Wifi {.no-padding}
```{r}
renderPlot({
  text <- format(state.agg.2017.sub()$districts_wifi_sample - state.agg.2017.sub()$districts_with_wifi, big.mark = ",", nsmall = 0, scientific = FALSE)
  ggplot() + ylim(24, 26) + annotate("text",  x = 2.5, y = 25.15, label = text, size = 20, color = "white") +
    theme(panel.background = element_rect(fill = colors$color[colors$label == 'wifi3']),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank())
})
```




Deep Dive SotS15 {.hidden data-orientation=rows}
=====================================================================
Row 
---------------------------------------------------------------------
### 
```{r}
renderValueBox(valueBox(state_name_caps, paste("Date Updated:", date.updated, sep=" ")))
```

### SotS 2015 Districts
```{r}
renderValueBox({
  val1 <- format(state.agg.sots.2016.sub()$sots15_districts_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.sots.2016.sub()$sots15_districts_pop, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'districts'])
})
```

### SotS 2015 Schools
```{r}
renderValueBox({
  val1 <- format(state.agg.sots.2016.sub()$sots15_schools_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.sots.2016.sub()$sots15_schools_pop, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'schools'])
})
```

### SotS 2015 Students
```{r}
renderValueBox({
  val1 <- format(state.agg.sots.2016.sub()$sots15_students_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.sots.2016.sub()$sots15_students_pop, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'students'])
})
```

Row {data-height=350}
---------------------------------------------------------------------
### SotS 2015 Clean Status {.no-title} 
```{r}
renderHighchart({
  highchart() %>% hc_chart(type = "solidgauge", backgroundColor = "white", marginTop = 50) %>% 
    hc_title(text = "SotS 2015 Clean Status", style = list(fontSize = "24px")) %>% 
    hc_tooltip(borderWidth = 0, backgroundColor = 'none', shadow = FALSE,style = list(fontSize = '16px'),
               pointFormat = '{series.name}<br><span style="font-size:2em; color: {point.color}; font-weight: bold">{point.y}%</span>',
               positioner = JS("function (labelWidth, labelHeight) {return{x: 200 - labelWidth / 2, y: 180};}")) %>% 
    hc_pane(startAngle = 0, endAngle = 360,
            background = list(list(outerRadius = '112%', innerRadius = '88%',
                                   backgroundColor = JS("Highcharts.Color('#009296').setOpacity(0.1).get()"), borderWidth =  0),
        list(outerRadius = '87%', innerRadius = '63%',
             backgroundColor = JS("Highcharts.Color('#F26B21').setOpacity(0.1).get()"), borderWidth = 0),
        list(outerRadius = '62%', innerRadius =  '38%',
             backgroundColor = JS("Highcharts.Color('#FDB913').setOpacity(0.1).get()"), borderWidth = 0))) %>% 
    hc_yAxis(min = 0, max = 100, lineWidth = 0, tickPositions = list()) %>% 
    hc_plotOptions(solidgauge = list(borderWidth = '34px', dataLabels = list(enabled = FALSE), linecap = 'round', stickyTracking = FALSE)) %>% 
    hc_add_series(name = "Districts", borderColor = JS("Highcharts.Color('#009296').get()"),
                  data = list(list(color = JS("Highcharts.Color('#009296').get()"), radius = "100%", innerRadius = "100%",
                                   y = state.agg.sots.2016.sub()$sots15_districts_sample_perc))) %>% 
    hc_add_series(name = "Schools", borderColor = JS("Highcharts.Color('#F26B21').get()"),
                  data = list(list(color = JS("Highcharts.Color('#F26B21').get()"), radius = "75%", innerRadius = "75%",
                                   y = state.agg.sots.2016.sub()$sots15_schools_sample_perc))) %>% 
    hc_add_series(name = "Students", borderColor = JS("Highcharts.Color('#FDB913').get()"),
                  data = list(list(color = JS("Highcharts.Color('#FDB913').get()"), radius = "50%", innerRadius = "50%",
                                   y = state.agg.sots.2016.sub()$sots15_students_sample_perc)))})
```

Row
---------------------------------------------------------------------
```{r}
#output$downloadData_SotS15_districts <- downloadHandler(filename = function(){paste('current15_districts.csv')},
#                                                    content = function(file){write.csv(current15_ct_sub(), file, row.names=F)})
#downloadLink("downloadData_SotS15_districts", label = "Download Table")

#renderDataTable({
#   if (input$state == 'ALL'){
#   datatable(current15_ct(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
#                  filter = 'top') 
# } else{
#   datatable(current15_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
#                  filter = 'top')
#}
#})
```



Deep Dive SotS16 {.hidden data-orientation=rows}
=====================================================================
Row 
---------------------------------------------------------------------
### 
```{r}
renderValueBox(valueBox(state_name_caps, paste("Date Updated:", date.updated, sep=" ")))
```

### SotS 2016 Districts
```{r}
renderValueBox({
  val1 <- format(state.agg.sots.2016.sub()$current16_districts_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.sots.2016.sub()$current16_districts_pop, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'districts'])
})
```

### SotS 2016 Schools
```{r}
renderValueBox({
  val1 <- format(state.agg.sots.2016.sub()$current16_schools_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.sots.2016.sub()$current16_schools_pop, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'schools'])
})
```

### SotS 2016 Students
```{r}
renderValueBox({
  val1 <- format(state.agg.sots.2016.sub()$current16_students_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.sots.2016.sub()$current16_students_pop, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'students'])
})
```

Row {data-height=350}
---------------------------------------------------------------------
### SotS 2016 Clean Status {.no-title} 
```{r}
renderHighchart({
  highchart() %>% hc_chart(type = "solidgauge", backgroundColor = "white", marginTop = 50) %>% 
    hc_title(text = "SotS 2016 Clean Status", style = list(fontSize = "24px")) %>% 
    hc_tooltip(borderWidth = 0, backgroundColor = 'none', shadow = FALSE,style = list(fontSize = '16px'),
               pointFormat = '{series.name}<br><span style="font-size:2em; color: {point.color}; font-weight: bold">{point.y}%</span>',
               positioner = JS("function (labelWidth, labelHeight) {return{x: 200 - labelWidth / 2, y: 180};}")) %>% 
    hc_pane(startAngle = 0, endAngle = 360,
            background = list(list(outerRadius = '112%', innerRadius = '88%',
                                   backgroundColor = JS("Highcharts.Color('#009296').setOpacity(0.1).get()"), borderWidth =  0),
        list(outerRadius = '87%', innerRadius = '63%',
             backgroundColor = JS("Highcharts.Color('#F26B21').setOpacity(0.1).get()"), borderWidth = 0),
        list(outerRadius = '62%', innerRadius =  '38%',
             backgroundColor = JS("Highcharts.Color('#FDB913').setOpacity(0.1).get()"), borderWidth = 0))) %>% 
    hc_yAxis(min = 0, max = 100, lineWidth = 0, tickPositions = list()) %>% 
    hc_plotOptions(solidgauge = list(borderWidth = '34px', dataLabels = list(enabled = FALSE), linecap = 'round', stickyTracking = FALSE)) %>% 
    hc_add_series(name = "Districts", borderColor = JS("Highcharts.Color('#009296').get()"),
                  data = list(list(color = JS("Highcharts.Color('#009296').get()"), radius = "100%", innerRadius = "100%",
                                   y = state.agg.sots.2016.sub()$current16_districts_sample_perc))) %>% 
    hc_add_series(name = "Schools", borderColor = JS("Highcharts.Color('#F26B21').get()"),
                  data = list(list(color = JS("Highcharts.Color('#F26B21').get()"), radius = "75%", innerRadius = "75%",
                                   y = state.agg.sots.2016.sub()$current16_schools_sample_perc))) %>% 
    hc_add_series(name = "Students", borderColor = JS("Highcharts.Color('#FDB913').get()"),
                  data = list(list(color = JS("Highcharts.Color('#FDB913').get()"), radius = "50%", innerRadius = "50%",
                                   y = state.agg.sots.2016.sub()$current16_students_sample_perc)))})
```

Row
---------------------------------------------------------------------
```{r}
#output$downloadData_SotS16_districts <- downloadHandler(filename = function(){paste('sots16_districts.csv')},
#                                                    content = function(file){write.csv(sots16_ct_sub(), file, row.names=F)})
#downloadLink("downloadData_SotS16_districts", label = "Download Table")

renderDataTable({
  if(input$state == 'ALL'){
    datatable(sots16_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
  }else{
    datatable(sots16_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
  }
})
```


Deep Dive Current17 {.hidden data-orientation=rows}
=====================================================================
Row 
---------------------------------------------------------------------
### 
```{r}
renderValueBox(valueBox(state_name_caps, paste("Date Updated:", date.updated, sep=" ")))
```

### Current 2017 Districts
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$districts_population, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'districts'])
})
```

### Current 2017 Schools
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$schools_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$schools_population, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'schools'])
})
```

### Current 2017 Students
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$students_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$students_population, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, "/", val2), color = colors$color[colors$label == 'students'])
})
```

Row {data-height=350}
---------------------------------------------------------------------
### Current 2017 Clean Status {.no-title} 
```{r}
renderHighchart({
  highchart() %>% hc_chart(type = "solidgauge", backgroundColor = "white", marginTop = 50) %>% 
    hc_title(text = "Current 2017 Clean Status", style = list(fontSize = "24px")) %>% 
    hc_tooltip(borderWidth = 0, backgroundColor = 'none', shadow = FALSE,style = list(fontSize = '16px'),
               pointFormat = '{series.name}<br><span style="font-size:2em; color: {point.color}; font-weight: bold">{point.y}%</span>',
               positioner = JS("function (labelWidth, labelHeight) {return{x: 200 - labelWidth / 2, y: 180};}")) %>% 
    hc_pane(startAngle = 0, endAngle = 360,
            background = list(list(outerRadius = '112%', innerRadius = '88%',
                                   backgroundColor = JS("Highcharts.Color('#009296').setOpacity(0.1).get()"), borderWidth =  0),
        list(outerRadius = '87%', innerRadius = '63%',
             backgroundColor = JS("Highcharts.Color('#F26B21').setOpacity(0.1).get()"), borderWidth = 0),
        list(outerRadius = '62%', innerRadius =  '38%',
             backgroundColor = JS("Highcharts.Color('#FDB913').setOpacity(0.1).get()"), borderWidth = 0))) %>% 
    hc_yAxis(min = 0, max = 100, lineWidth = 0, tickPositions = list()) %>% 
    hc_plotOptions(solidgauge = list(borderWidth = '34px', dataLabels = list(enabled = FALSE), linecap = 'round', stickyTracking = FALSE)) %>% 
    hc_add_series(name = "Districts", borderColor = JS("Highcharts.Color('#009296').get()"),
                  data = list(list(color = JS("Highcharts.Color('#009296').get()"), radius = "100%", innerRadius = "100%",
                                   y = round((state.agg.2017.sub()$districts_clean_ia_sample / state.agg.2017.sub()$districts_population)*100, 0)))) %>% 
    hc_add_series(name = "Schools", borderColor = JS("Highcharts.Color('#F26B21').get()"),
                  data = list(list(color = JS("Highcharts.Color('#F26B21').get()"), radius = "75%", innerRadius = "75%",
                                   y = round((state.agg.2017.sub()$schools_clean_ia_sample / state.agg.2017.sub()$schools_population)*100, 0)))) %>% 
    hc_add_series(name = "Students", borderColor = JS("Highcharts.Color('#FDB913').get()"),
                  data = list(list(color = JS("Highcharts.Color('#FDB913').get()"), radius = "50%", innerRadius = "50%",
                                   y = round((state.agg.2017.sub()$students_clean_ia_sample / state.agg.2017.sub()$students_population)*100, 0))))})
```

Row
---------------------------------------------------------------------
```{r}
#output$downloadData_17_districts <- downloadHandler(filename = function(){paste('current17_districts.csv')},
#                                                    content = function(file){write.csv(current17_ct_sub(), file, row.names=F)})
#downloadLink("downloadData_17_districts", label="Download Table")

renderDataTable({
  if (input$state == 'ALL'){
    datatable(current17_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
  } else{
    datatable(current17_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
  }
})
```


Deep Dive Upgrades {.hidden data-orientation=rows}
===========================================================================
Row
---------------------------------------------------------------------
```{r}
#output$downloadData_upgrades <- downloadHandler(
#  filename = function() {paste('upgrades_deep_dive.csv')},
#  content = function(file) {
#      write.csv(upgrades_ct_sub(), file, row.names=F)
#  })
# downloadLink("downloadData_upgrades", label = "Download Table")

renderDataTable({
  if(input$state == 'ALL'){
    datatable(upgrades_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  } else{
    datatable(upgrades_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  }
})
```



Deep Dive Connectivity {.hidden data-orientation=rows}
=====================================================================
Row 
---------------------------------------------------------------------
### 
```{r}
renderValueBox(valueBox(state_name_caps, paste("Date Updated:", date.updated, sep=" ")))
```

### Current 2017 Districts Meeting Goal
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$districts_meeting_2014_bw_goal, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, val2, sep=' / '), color = colors$color[colors$label == 'districts'])
})
```

### Current 2017 Schools Meeting Goal
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$schools_meeting_2014_bw_goal, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$schools_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, val2, sep=' / '), color = colors$color[colors$label == 'schools'])
})
```

### Current 2017 Students Meeting Goal
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$students_meeting_2014_bw_goal, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$students_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, val2, sep=' / '), color = colors$color[colors$label == 'students'])
})
```

Row
---------------------------------------------------------------------
```{r}
#output$downloadData_connectivity <- downloadHandler(
#  filename = function() {paste('connectivity_deep_dive.csv')},
#  content = function(file) {
#    write.csv(connectivity_ct_sub(), file, row.names=F)})
#downloadLink("downloadData_connectivity", label="Download Table")

renderDataTable({
  if (input$state == 'ALL'){
    datatable(connectivity_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  } else{
    datatable(connectivity_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  }
})
```


Deep Dive Fiber {.hidden data-orientation=columns}
=====================================================================
Column
---------------------------------------------------------------------
```{r}
#output$downloadData_fiber <- downloadHandler(
#  filename = function() {paste('fiber_deep_dive.csv')},
#  content = function(file) {
#    write.csv(fiber_ct_sub(), file, row.names=F)
#  })
#downloadLink("downloadData_fiber", label="Download Table")

renderDataTable({
  if (input$state == 'ALL'){
    datatable(fiber_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  } else{
    datatable(fiber_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  }
})
```



Deep Dive Affordability {.hidden data-orientation=rows}
=====================================================================
Row 
---------------------------------------------------------------------
### 
```{r}
renderValueBox(valueBox(state_name_caps, paste("Date Updated:", date.updated, sep=" ")))
```

### Current 2017 Districts Meeting Goal
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$districts_meeting_affordability, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$districts_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, val2, sep=' / '), color = colors$color[colors$label == 'districts'])
})
```

### Current 2017 Schools Meeting Goal
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$schools_meeting_affordability, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$schools_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, val2, sep=' / '), color = colors$color[colors$label == 'schools'])
})
```

### Current 2017 Students Meeting Goal
```{r}
renderValueBox({
  val1 <- format(state.agg.2017.sub()$students_meeting_affordability, big.mark = ",", nsmall = 0, scientific = FALSE)
  val2 <- format(state.agg.2017.sub()$students_clean_ia_sample, big.mark = ",", nsmall = 0, scientific = FALSE)
  valueBox(paste(val1, val2, sep=' / '), color = colors$color[colors$label == 'students'])
})
```

Row
---------------------------------------------------------------------
###
```{r}
 #output$downloadData_affordability <- downloadHandler(
 #filename = function(){paste('affordability_deep_dive.csv')},
 #content = function(file){
 #  write.csv(affordability_ct_sub(), file, row.names=F)})
 #downloadLink("downloadData_affordability", label = "Download Table")

renderDataTable({
  if (input$state == 'ALL'){
    datatable(affordability_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  } else{
    datatable(affordability_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE), filter = 'top')
  }
})
```

Deep Dive Wifi {.hidden data-orientation=rows}
=====================================================================
Row 
---------------------------------------------------------------------
```{r}
renderDataTable({
  if (input$state == 'ALL'){
    datatable(wifi_ct, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE), filter = 'top')
  } else{
    datatable(wifi_ct_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE), filter = 'top')
  }
})
```


Target Lists Connectivity {.hidden data-orientation=rows}
============================================================================

### Targets and Potential Targets
```{r}
 output$downloadData_connectivity <- downloadHandler(
  filename = function() {paste('connectivity_target_list.csv')},
  content = function(file){
    if (input$state == 'ALL'){
      write.csv(connectivity_tar, file, row.names=F)
    } else{
      write.csv(connectivity_tar_sub(), file, row.names=F)
    }
  })
 downloadLink("downloadData_connectivity", label = "Download Table")
 
 renderDataTable({
   if (input$state == 'ALL'){
     datatable(connectivity_tar, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
   } else{
     datatable(connectivity_tar_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
               filter = 'top')
   }
})
```



Target Lists Fiber {.hidden data-orientation=rows}
============================================================================

### Targets and Potential Targets
```{r}
 output$downloadData_fiber <- downloadHandler(
  filename = function() {paste('fiber_target_list.csv')},
  content = function(file){
    if (input$state == 'ALL'){
      write.csv(fiber_tar, file, row.names=F)
    } else{
      write.csv(fiber_tar_sub(), file, row.names=F)
    }
  })
 downloadLink("downloadData_fiber", label = "Download Table")
 
 renderDataTable({
   if (input$state == 'ALL'){
     datatable(fiber_tar, rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
   } else{
     datatable(fiber_tar_sub(), rownames=FALSE, escape=FALSE, options=list(paging=TRUE, searching=TRUE, scrollX=TRUE, fixed=TRUE),
                  filter = 'top')
   }
})
```


